Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
VSTTE 2020 paper update

\begin{figure}[h]
\includegraphics[width=0.9\textwidth]{optimalsizingprocess4}
\centering
\caption{Comparison of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.75\textwidth]{fig2_rev2.jpg}
\end{center}
%
%\begin{wrapfigure}{r}{0.5\textwidth}
%\begin{center}
%	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
%\end{center}	
	\caption{CEGIS in PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
%\end{wrapfigure}
\end{figure}

@@

%\begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}

@@

\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries, usually is a design definition and has a value ranging from $0.5$ to $2$ days. $DOD$ is the 
the depth of discharge or the fraction of discharge (usually 25\% for lead-acid batteries, and 80\% for lithium batteries). However it is worth to separate the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours). Therefore, here in this thesis, the definition given here is for maximum $DOD$. When we deal with daily $DOD$ we will call it of $DOD_{day}$, and obviously the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.

@@

The inverter sizing check is performed through three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.

@@

\textcolor{red}{could you condense this algorithm by joining lines 5 to 8?}

%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \REQUIRE weather data (temperature, solar irradiance); list of PV panels, controllers, batteries, and inverters datasheet information and cost; design requirements (load curve, peak demand, load surge power, daily energy consumption, battery autonomy, AC voltage); design assumptions (battery state of charge, depth of discharge, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
  \STATE Initialize variables \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
  \FOR {$HintCost=MinCost$ to $MaxCost$} 
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}
%
Our synthesis algorithm will synthesize constant values; 
it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers and inverters. Moreover, we define design (house) requirements and design assumptions.

The \textit{for}-loop started at line $4$ controls the lowest cost of the PV solution. In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $21$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). The $MaxCost$ value at line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $5$ to $8$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements. A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.

Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$). The directive \textit{assume} (lines $11$, $16$, $17$ and $18$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of lines $11$, $16$, $17$ and $18$. Line $11$ is specific to PV panels. Line $16$ is for the battery bank. Line $17$ is the charge controller voltage check. Line $18$ does the inverter check and ensures the power demand and the surge power of the inverter.
Therefore, our synthesis algorithm reaches line $19$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $20$). This cost is the equivalent to~\ref{eq:LCC}.

@@

The results are presented in Table~\ref{tab1}. 
%
\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;        NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
\end{scriptsize}
\end{table}
%
The violation (SAT result) indicated all over the Table~\ref{tab1} 
is the $assert$ of the line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.

@@

Here we used ESBMC in incremental BMC configuration with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours. 
%Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated. 
ESBMC with this configuration was unable to obtain an optimal solution in cases $2$ and $7$. Case $2$ reached a \textit{time out} result after $11$ hours. Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was unable to provide a feasible solution considering the equipment list \textcolor{red}{why? is it a bug in ESBMC?}. This UNSAT situation was reached in less than one minute.
%
%\begin{figure}[h]
%\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
%\centering
%\caption{ESBMC counterexample for case 3 optimization.}
%\label{fig:esbmcoptcase3}
%\end{figure}
%
These experimental results partially answers the \textit{EG2} \textcolor{red}{why ``partially''? explain here}.

@@

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced. %According to PVsyst, we have to each case study:
%
%\begin{itemize}
 For case study 1, PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct. Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary.
For case study 2, PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution. Only HOMER Pro was left for comparison. However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary.

>>>>

\begin{figure}[h]
\fbox{\includegraphics[width=0.9\textwidth]{optimalsizingprocess4}}
\centering
\caption{Comparison of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\fbox{\includegraphics[width=0.75\textwidth]{fig2_rev2.jpg}}
\end{center}
%
%\begin{wrapfigure}{r}{0.5\textwidth}
%\begin{center}
%	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
%\end{center}	
	\caption{CEGIS in PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
%\end{wrapfigure}
\end{figure}

@@

%\begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[h]
\fbox{\includegraphics[width=0.8\textwidth]{blockdiagramPVS2_rev}}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}

@@

\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries, usually is a design definition and has a value ranging from $0.5$ to $2$ days. $DOD$ is the 
the depth of discharge or the fraction of discharge. The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge (SOC) of $75$\% and $20$\% respectively, because $SOC=1-DOD$. However it is worth to separate the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours). Therefore, here in this thesis, the definition given here is for maximum $DOD$. When we deal with daily $DOD$ we will call it of $DOD_{day}$, and obviously the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.

@@

The inverter sizing check is performed through three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load, i.e. the outlet voltage. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.

@@

 \begin{algorithm}[h]
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \REQUIRE weather data (temperature, solar irradiance); data from panels, controllers, batteries, and inverters; design requirements (load curve, peak demand, load surge power, energy consumption, battery autonomy, AC voltage); design assumptions (SOC, DOD, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
  \STATE Initialize variables \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
  \FOR {$HintCost=MinCost$ to $MaxCost$} 
 	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
% 	\STATE Declare non-deterministic variable to select Controller from list \\
% 	\STATE Declare non-deterministic variable to select Battery from list \\
% 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}

Our synthesis algorithm will synthesize constant values; 
it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers and inverters. Moreover, we define design (house) requirements and design assumptions.

The \textit{for}-loop started at line $4$ controls the lowest cost of the PV solution. In particular, it starts with cost $MinCost$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). The $MaxCost$ value at line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (line $5$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements. A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.

Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$). The directive \textit{assume} (lines $8$, $13$, $14$ and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines. Line $5$ is specific to PV panels. Line $13$ is for the battery bank. Line $14$ is the charge controller voltage check. Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$). This cost is the equivalent to~\ref{eq:LCC}.

@@

The results are presented in Table~\ref{tab1}. 
%
\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;        NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
\end{scriptsize}
\end{table}
%
The violation (SAT result) indicated all over the Table~\ref{tab1} 
is the $assert$ of the line $18$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.

@@

Here we used ESBMC in incremental BMC configuration with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours. 
%Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated. 
ESBMC with this configuration was unable to obtain an optimal solution in cases $2$ and $7$. Case $2$ produced a \textit{time out}. Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was unable to provide a feasible solution. However this is not a bug, and it means that the available list of equipment can not produce an feasible solution that satisfies electrical compatibility or the design requirements. This UNSAT situation was reached in less than one minute.
%
%\begin{figure}[h]
%\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
%\centering
%\caption{ESBMC counterexample for case 3 optimization.}
%\label{fig:esbmcoptcase3}
%\end{figure}
%
These experimental results answers the \textit{EG2}.

@@

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced. %According to PVsyst, we have to each case study:
\textcolor{red}{do you think whether it is possible to summarise these results in a table?}
%
%\begin{itemize}
 For case study 1, PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct. Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary.
For case study 2, PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution. Only HOMER Pro was left for comparison. However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary.
